Historical Soil Organic Carbon Budget

### 2020-04-03 SOCbudgetPaper/SOCbudget.tex
include figures in pdf and docx

>>>>

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-1} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-2} \caption{two column figure}\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-3} \caption{two column figure}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/RegionPlot+Valid} \caption{two column figure}\label{fig:unnamed-chunk-9}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CShare_1965} \includegraphics[width=12cm]{images/maps/CShare_2010} \caption{two column figure}\label{fig:unnamed-chunk-10}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CIncrease_1965} \includegraphics[width=12cm]{images/maps/CIncrease_2010} \caption{two column figure}\label{fig:unnamed-chunk-11}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CShare_4ColorClimates} \caption{one column figure}\label{fig:unnamed-chunk-12}
\end{figure}
\newpage
